Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
adding comments.
brush up comment.
adding a comment.

@@

@@

\begin{quote}\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.
\end{itemize} \end{quote}

>>>>

\begin{quote}
kazu: the two paragraphs above doe not seem logical to me. I would change these
as follows:

BDD tools can be used to document the behavior of a system in a way that
is similar to a specification.  All facets of the system should be
described with evidence, including every possible corner case.

We think that some evidence is useful as user documentation, hence we
want to be able to include it in Haddock comments.  But others are not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.
They should be included in code document. Both kinds of evidence
should be automatically tested.
\end{quote}

@@

\begin{quote}
    \emph{kazu: We should explicitly repeat that we propose to Doctest as a BDD tool here..}
\end{quote}

@@

\begin{quote}
\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.

    \emph{kazu: I guess that it's enough to describe this in the Implementation Section.}
\end{itemize}
\end{quote}
